Sampling-Based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex
reconstruction of tunnels

One tunnel is defined by an exit point and by an active site.
If both these nodes are connected to the same component of the graph, they define a static tunnel.
Such a tunnel can be reconstructed simply by finding a path between these two nodes in the graph.
If there does not exist any path between the exit point $p \in P^i$ (exit point at frame $i$) and the active site $\qinit^i$ in the same frame, the dynamic tunnel has to start from a different active site (in one of the previous frames).
A path from $p$ to the first active site reachable in the graph (measured by the number of edges) describes the dynamic tunnel.
An example is depicted in Fig.~\ref{fig::components}.

@@

\begin{table}
\centering
\caption{\label{tab::dyn} The number of frames with detected dynamic tunnels. The number of frames
    with static tunnels, detected by CAVER 3.0.
}
\begin{tabular}{ccccc}
\toprule
  \multirow{2}{*}{ Dynamic tunnel}   &  \multicolumn{2}{c}{ Static tunnels}   \\
                                     &  {\bf Exists} & {\bf Not exists} \\
\midrule                                     
{\bf End of tunnel/cavity}           & 1,324/661 & 1,027/725  \\
{\bf Static tunnel}                  & 3,118     &  0   \\
{\bf No tunnel}                      & 669      & 1,833    \\ 
\bottomrule                                 
\end{tabular}
\end{table}

>>>>

One tunnel is defined by an exit point and by an active site.
A static tunnels is contained completely in one frame, therefore the path from $p \in P^i$ to $\qinit \in \CF^i$ in the graph
$G$ describes it.
Dynamic tunnels have active site and exit point in different frame, so to reconsruct them,
a path from $p \in P^i$ the first reachable $\qinit \in \CF^j, j < i$ has to be searched in the grapg $G$.
%If both these nodes are connected to the same component of the graph, they define a static tunnel.
%Such a tunnel can be reconstructed by finding a path between these two nodes in the graph.
%If there does not exist any path between the exit point $p \in P^i$ (exit point at frame $i$) and the active site $\qinit^i$ in the same frame, the dynamic tunnel has to start from a different active site (in one of the previous frames).
%A path from $p$ to the first active site reachable in the graph (measured by the number of edges) describes the dynamic tunnel.
An example is depicted in Fig.~\ref{fig::components}.

@@

\begin{table}
\centering
\caption{\label{tab::dyn} The number of frames with detected dynamic tunnels. 
    %The number of frames with static tunnels, detected by CAVER 3.0.
}
\begin{tabular}{ccccc}
\toprule
  \multirow{2}{*}{ Proposed method}   &  \multicolumn{2}{c}{ Static tunnels}   \\
                                     &  {\bf Exists} & {\bf Not exists} \\
\midrule                                     
{\bf End of tunnel/cavity}           & 1,324/661 & 1,027/725  \\
{\bf Static tunnel}                  & 3,118     &  0   \\
{\bf No tunnel}                      & 669      & 1,833    \\ 
\bottomrule                                 
\end{tabular}
\end{table}
